### 2023-11-27 design/crossbar.tex
corrected a few things

This design is the one that is used in \cite{doubleMem}. Let's assume that a given memristor has a resistance range of $R\in[R_{min},R_{max}]$, that means its conductance range is $\sigma \in [\sigma_{min},\sigma_{max}]$ (with $\sigma_{min}= \frac{1}{R_{max}}$ and $\sigma_{max}= \frac{1}{R_{min}}$). This design works using two \ac{opAmp} connected to $V_{cm}$ with the positive pin and the negative pin to the output of the crossbar array. \Cref{eq:doubleMem0,eq:doubleMem1,eq:doubleMem2} are describing how this architecture works. A simplified version of the double memristors per synapse circuit is also available in \cref{circt:doubleMem}.

@@

\begin{equation}
  \label{eq:doubleMem0}
  V_{opAmp_0}=-R_r\cdot i_+
\end{equation}
\begin{equation}
  \label{eq:doubleMem1}
  i_{R_f}=i_-+\frac{V_{opAmp_0}}{R_r}=i_--i_+
\end{equation}
\begin{equation}
  \label{eq:doubleMem2}
  V_{opAmp_1}=y_0=-R_f\cdot(i_--i_+)=R_f\cdot(i_+-i_-)=R_f\cdot\sum_{k=0}^n(\sigma_{k+}-\sigma_{k-})\cdot x_k
\end{equation}
With $i_+=\sum_{k=0}^n\sigma_{k+}\cdot x_k$ and $i_-=\sum_{k=0}^n\sigma_{k-}\cdot x_k$.

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|}
    \cline{2-3}
    \rowcolor{gray}
    \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFFF}} & Two memristors per synapse & One memristor per synapse \\
    \hline
    Maximum weight & $\sigma_{max}-\sigma_{min}$ & $\sigma_{max} -\overline{\sigma}$\\
    \hline
    Minimum weight & $\sigma_{min}-\sigma_{max}$ & $\sigma_{min} -\overline{\sigma}$\\
    \hline
    Range & $2\cdot(\sigma_{max}-\sigma_{min})$&$\sigma_{max}-\sigma_{min}$\\
    \hline
  \end{tabular}
  \caption{Synaptic weights precision (extracted from \cite{doubleMem})}
  \label{tab:synapses}
\end{table}

>>>>

This design is the one that is used in \cite{doubleMem}. Let's assume that a given memristor has a resistance range of $R\in[R_{min},R_{max}]$, that means its conductance range is $ G \in [ G_{min}, G_{max}]$ (with $ G_{min}= \frac{1}{R_{max}}$ and $ G_{max}= \frac{1}{R_{min}}$). This design works using two \ac{opAmp} connected to $V_{cm}$ with the positive pin and the negative pin to the output of the crossbar array. \Cref{eq:doubleMem0,eq:doubleMem1,eq:doubleMem2} are describing how this architecture works. A simplified version of the double memristors per synapse circuit is also available in \cref{circt:doubleMem}.

@@

\begin{equation}
  \label{eq:doubleMem0}
  V_{opAmp_0}=-R_r\cdot i_+
\end{equation}
\begin{equation}
  \label{eq:doubleMem1}
  i_{R_f}=i_-+\frac{V_{opAmp_0}}{R_r}=i_--i_+
\end{equation}
\begin{equation}
  \label{eq:doubleMem2}
  V_{opAmp_1}=y_0=-R_f\cdot(i_--i_+)=R_f\cdot(i_+-i_-)=R_f\cdot\sum_{k=0}^n( G_{k+}- G_{k-})\cdot x_k
\end{equation}
With $i_+=\sum_{k=0}^n G_{k+}\cdot x_k$ and $i_-=\sum_{k=0}^n G_{k-}\cdot x_k$.

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|}
    \cline{2-3}
    \rowcolor{gray}
    \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFFF}} & Two memristors per synapse & One memristor per synapse \\
    \hline
    Maximum weight & $ G_{max}- G_{min}$ & $ G_{max} -\overline{ G}$\\
    \hline
    Minimum weight & $ G_{min}- G_{max}$ & $ G_{min} -\overline{ G}$\\
    \hline
    Range & $2\cdot( G_{max}- G_{min})$&$ G_{max}- G_{min}$\\
    \hline
  \end{tabular}
  \caption{Synaptic weights precision (extracted from \cite{doubleMem})}
  \label{tab:synapses}
\end{table}

### 2023-11-27 design/memcell.tex
Renamed files and folder
area stuff
Worked on paper+corrected errors
corrected a few things

@@

For this circuit the approximate onChip area :

With $A_{CMOS} = w\cdot l = 2\cdot 10^{-7} \cdot 6 \cdot 10^{-8} = 1.2 \cdot 10^{-14} m^2$

@@

\begin{figure}[H]
  \centering
  \includesvg[height=2.5cm]{memcell/memcellSymbol}
  \caption{Memory cell symbol with the input enable pin (top) and the output enable pin (bottom). The left and right pins are interchangebly the input and ouput for the sake of readability}
  \label{circt:memcell}
\end{figure}

>>>>

The \ac{CMOS} switches found in the circuit have width of $w=200nm$ and a length of $l=60nm$.

@@

@@

\begin{figure}[H]
  \centering
  \includesvg[height=2.5cm]{memcell/memcellSymbol}
  \caption{Memory cell symbol with the input enable pin (top) and the output enable pin (bottom). The left and right pins can be either input or output. The component is non-linear.}
  \label{sym:memcell}
\end{figure}

For this circuit the approximate onChip area is :

With $A_{CMOS} = w\cdot l$

### 2023-11-27 design/run.tex
corrected a few things

In order to run the simulation some variables need to be set. The time step ($T$) value was chosen to be $T=8\mu s$, the pause between two \ac{LSTM} steps is set to be $\frac{T}{8}=1\mu s$. The value for the maximum and minimum resistances value of the memristor used ($R_{max}$ and $R_{min}$, respectively) are set to be in acordance with the \textbf{KNOWN}'s memristors. The resistance values used for the simulation are thus $R_{max}=10^6 \Omega=1M\Omega$ and $R_{min}=10^4 \Omega = 10k\Omega$.

>>>>

In order to run the simulation some variables need to be set. The time step ($T$) value was chosen to be $T=8\mu s$, the pause between two \ac{LSTM} steps is set to be $\frac{T}{8}=1\mu s$. The value for the maximum and minimum resistances value of the memristor used ($R_{max}$ and $R_{min}$, respectively) are set to be in acordance with the \textbf{KNOWM}\textregistered{}'s memristors \cite{Knowm}. The resistance values used for the simulation are thus $R_{max}=10^6 \Omega=1M\Omega$ and $R_{min}=10^4 \Omega = 10k\Omega$.

### 2023-11-27 state/crossbar.tex
corrected a few things

\begin{equation}
  V_i = R\cdot I_{i} \Rightarrow I_{i} = V_i\cdot (\frac{1}{R})= V_i\cdot\sigma_i
\end{equation}
With $\sigma_i$ being the conductance of memristor, defined as $\sigma_i=\frac{1}{R_i}$.

This line then joins the column where a current of $I_{i,j-1}$ is flowing, then according to Kirchhoff's current law the resulting current is :
\begin{equation}
  I_{j,i} = I_{j,i-1}+I_{i} = I_{j,i-1} + V_i\cdot\sigma_i
\end{equation}
By applying this process to the whole system we find that the current at the bottom of one column is :
\begin{equation}
  I_1=\sigma_1\cdot V_1 + \sigma_2\cdot V_2 + \sigma_3\cdot V_3
\end{equation}
With $\sigma_1$, $\sigma_2$ and $\sigma_3$ being the conductance of the 3 memristors in the first column.

>>>>

\begin{equation}
  V_i = R\cdot I_{i} \Rightarrow I_{i} = V_i\cdot (\frac{1}{R})= V_i\cdot G_i
\end{equation}
With $G_i$ being the conductance of memristor, defined as $ G_i=\frac{1}{R_i}$.

This line then joins the column where a current of $I_{i,j-1}$ is flowing, then according to Kirchhoff's current law the resulting current is :
\begin{equation}
  I_{j,i} = I_{j,i-1}+I_{i} = I_{j,i-1} + V_i\cdot G_i
\end{equation}
By applying this process to the whole system we find that the current at the bottom of one column is :
\begin{equation}
  I_1= G_1\cdot V_1 +  G_2\cdot V_2 +  G_3\cdot V_3
\end{equation}
With $G_1$, $G_2$ and $G_3$ being the conductance of the 3 memristors in the first column.
